Stability in human interaction networks: primitive typology of vertex, prominence of measures and activity statistics

### 2015-04-02 paper.tex
terminada parte principal da formalizacao da setorializacao de Erdos

% Use this file as a source of example code for your aip document.
% Use the file aiptemplate.tex as a template for your document.
\documentclass[%
 aip,
 jmp,%
 amsmath,amssymb,
%preprint,%
 reprint,%
%author-year,%
%author-numerical,%
]{revtex4-1}

\usepackage{graphicx}% Include figure files
\usepackage{grffile}
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines
\usepackage{multirow}
\usepackage{color} % for the notes
\usepackage{etex}
\reserveinserts{58}
\usepackage{morefloats}
\usepackage{hyperref}
\usepackage{xcolor}
\hypersetup{
        colorlinks,
        linkcolor={red!50!black},
        citecolor={blue!50!black},
        urlcolor={blue!80!black}
}

@@

\begin{alignat}{3}
e_{\sigma,1}&=\{\;i\;|\;\overline{k}_{\sigma,\Leftarrow}\geq&&\overline{k}_{\sigma,i}\} \\
e_{\sigma,2}&=\{\;i\;|\;\overline{k}_{\sigma,\Leftarrow}<\;&&\overline{k}_{\sigma,i}\leq\overline{k}_{\sigma,\Rightarrow}\} \\ 
e_{\sigma,3}&=\{\;i\;|\;&&\overline{k}_{\sigma,i}<\overline{k}_{\sigma,\Rightarrow}\}
\end{alignat}

@@

These compound criteria, and the simplification of all the compound possibilities as listed above (into exclusivist/inclusivist criterion/cascade/externals), can be formalized in strict mathematical terms, but this was considered out of the scope of the present article. Notice that the exclusivist cascade is the same sectioning that an inclusivist cascade from periphery to hubs (inverted order of precedence). Important here is to notice that compound criteria can be used to examine network sections in the case of a low number of messages, such as in the last figures of Appendix~\ref{figures}.

>>>>

% Use this file as a source of example code for your aip document.
% Use the file aiptemplate.tex as a template for your document.
\documentclass[%
 aip,
 jmp,%
 amsmath,amssymb,
%preprint,%
 reprint,%
%author-year,%
%author-numerical,%
]{revtex4-1}
\usepackage{graphicx}% Include figure files
\usepackage{grffile}
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines
\usepackage{multirow}
\usepackage{color} % for the notes
\usepackage{etex}
\reserveinserts{58}
\usepackage{morefloats}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{amsmath}
\hypersetup{
        colorlinks,
        linkcolor={red!50!black},
        citecolor={blue!50!black},
        urlcolor={blue!80!black}
}

@@

\begin{alignat}{3}\label{eq:part}
e_{\sigma,1}&=\{\;i\;|\;\overline{k}_{\sigma,\Leftarrow}\geq&&\overline{k}_{\sigma,i}\} \nonumber \\
e_{\sigma,2}&=\{\;i\;|\;\overline{k}_{\sigma,\Leftarrow}<\;&&\overline{k}_{\sigma,i}\leq\overline{k}_{\sigma,\Rightarrow}\} \\ 
e_{\sigma,3}&=\{\;i\;|\;&&\overline{k}_{\sigma,i}<\overline{k}_{\sigma,\Rightarrow}\} \nonumber
\end{alignat}

@@

Using equations~\ref{eq:part}, these compound criteria $C_\delta$, with $\delta$ integer in the interval $1<\delta<6$ can be described as:

%\begin{alignat}{3}
\begin{equation}
\begin{split}
%\begin{multline}
C_1&=\{c_{1,\phi}=\left\{i\mid i\;\in e_{\sigma,\phi}, \;\forall\; \sigma\}\right\} \\
C_2&=\{c_{2,\phi}=\left\{i\mid \exists \;\;\sigma : i \in e_{\sigma,\phi}\}\right\} \\
C_3&=\{c_{3,\phi}=\left\{i\mid i\;\in e_{\sigma,\phi'}, \;\forall\; \sigma,\;\forall\;\phi'\geq \phi\}\right\} \\
C_4&=\{c_{4,\phi}=\left\{i\mid i\;\in e_{\sigma,\phi'}, \;\forall\; \sigma,\;\forall\;\phi'\leq \phi\}\right\} \\
C_5&=\{c_{5,\phi}=\left\{i\mid i\;\in e_{\sigma,\phi'}, \;\forall\; \sigma,\right.\\
	  &\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \left.\;\forall\;(\phi'+1)\%4\leq (\phi+1)\%4\}\right\} \\
C_6&=\{c_{6,\phi}=\left\{i\mid i\;\in e_{\sigma,\phi'}, \;\forall\; \sigma,\right.\\
	  &\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \left.\;\forall\;(\phi'+1)\%4\geq (\phi+1)\%4\}\right\} \\
%\end{multline}
\end{split}
\end{equation}
%\end{alignat}

These compound criteria, and the simplification of all the compound possibilities as listed above (into exclusivist/inclusivist criterion/cascade/externals), can be formalized in strict mathematical terms, but this was considered out of the scope of the present article. Notice that the exclusivist cascade is the same sectioning that an inclusivist cascade from periphery to hubs (inverted order of precedence). Compound criteria can be used to examine network sections in the case of a low number of messages, such as in the last figures of Appendix~\ref{figures}.
